---
title: "Part 2 Wild Data"
author: "Andre Dextre"
format: html
editor: visual
execute: 
  warning: false
  messages: false
  echo: true
  eval: false
---

```{r}
library(tidyverse)
library(janitor)
library(skimr)
library(here)
```

## Part 2: Wild Data

What does each column contain?

What are the unit of each?

What is the study overall about?

```{r}
mack_verts <- read_csv(here::here("data", "AS00601.csv")) %>% clean_names()

```

```{r}
mc_wt_5 <- mack_verts$weight[5]

mc_wt_5
mc_length_8_20 <- mack_verts$length1[8:20]

mc_length_8_20

mc_dates <- mack_verts$sampledate

mc_dates
```

```{r}
mc_salamander <- mack_verts %>% dplyr::filter(species == "DITE")
```

```{r}
salamander_plot <- ggplot(data = mc_salamander, aes(x = length1,
                                 y = weight)) +
  geom_point(color = "dodgerblue2") +
  theme() +
  labs(x = "Length (mm)",
       y = "Weight (g)",
       title = "Salamander Proportions",
       caption = "The longer the salamander the heavier",
       subtitle = "Length (mm) vs Weight (g)")

ggsave(plot = salamander_plot, here("figs", "salamander_size.png"),
       width = 6,
       height = 5)
```


Make a cutthroat plot

Similar to above, make a subset called mc_trout that only contains observations for cutthroat trout (species “ONCL”)
Create a scatterplot of length1 by weight for all trout in the dataset
Customize so that the point color depends on reach
Customize your color scheme (e.g. scale_color_manual())
Facet your plot by creek reach (facet_wrap(~...))
Update graph axis labels and title
Export your graph as cutthroat_size.png to the figs folder